Handling String-Number Conversion in String Constraint Solving

### 2019-11-08 draft.tex
def of runs and accepting of autoamta

\usepackage{xcolor}
\usepackage{amssymb} 
\usepackage{tikz}
\usepackage[autostyle]{csquotes}
\usepackage{listings}
\synctex=1

@@

A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}. 
%The semantics of finite automaton is defined in the standard manner. 
A run of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_i)$
We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
\lh{If we later start technical talking about tings like runs then we should include this definition.}

>>>>

\usepackage{xcolor}
\usepackage{amssymb} 
\usepackage{tikz}
\usepackage[autostyle]{csquotes}
\usepackage{listings}
\usepackage{multirow}
\synctex=1

@@

A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}. 
%The semantics of finite automaton is defined in the standard manner. 
A \emph{run} of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$. The run  is \emph{accepting} if $q_0 = q_i$ and $q_i = q_f$ and $w$ then is \emph{accepted}.
The \emph{language} of $A$ is the set $L(A)$ of all accepted words.
